---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# neon4cast-shiny

## Overview

Source code for EFI-NEON Ecological Forecasting Challenge Dashboard Shiny app at [shiny.ecoforecast.org](https://shiny.ecoforecast.org/)


## Testing Shiny app locally

The code in `index.Rmd` that runs the app assumes the forecasts and target files are saved in local directories. Towards the top of `index.Rmd`

* `base.dir`: `"/efi_neon_challenge/forecasts/"`
* `target.dir`: `"/efi_neon_challenge/targets/"`

You can change these directory paths during local development, but be sure to revert them before merging to GitHub.


## Example using phenology forecasts

Here is an example on how to get the Shiny app running locally for the phenology forecasts:

1. Install the development version of the [`neon4cast`](https://github.com/eco4cast/neon4cast) R package from GitHub. In particular we need the [`download_forecast()`](https://github.com/eco4cast/neon4cast/blob/main/R/download_forecast.R) function.
    ```{r, eval = FALSE}
    # install.packages("remotes")
    remotes::install_github("eco4cast/neon4cast")
    ```
1. Download the phenology forecasts to the `base.dir`
    ```{r, eval = FALSE}
    library(neon4cast)
    download_forecast(theme = "phenology", dir = "/efi_neon_challenge/forecasts/")
    ```
1. Download the corresponding targets files on [data.ecoforecast.org/minio/targets/](https://data.ecoforecast.org/minio/targets/) to the `target.dir`. So for our phenology example:
    1. Go to the [phenology targets folder](https://data.ecoforecast.org/minio/targets/phenology/)
    1. Click on both `prov.json` and `phenology-targets.csv.gz` and download
    1. Move these files to to `/efi_neon_challenge/targets/phenology/`
1. Go to `index.Rmd` and click on "Run Document" to load the Shiny app
